UQWorld: an Applied UQ Community

### 2019-05-07 latex/BeamerGPR.tex
Update slide on the goal of our community

\begin{tabularx}{\textwidth}{XX}
  \hline
  Questions                            & Answers \\
  \hline
  \emph{What will the community be about?}               & About UQ and UQLab-related topics \\
  \emph{Who is the community for?}                       & UQ practitioners, researchers, and UQLab users \\

  \emph{What is the purpose or goal of the community? What UQLab community strive for?}
  & \tabitem Be a place to discuss about, share, learn, and get help in topics related to UQ, from beginners to advanced \\
  & \tabitem Be the definitive community-powered home for UQLab support and best practices \\

  \emph{What will happen in the community?}          & Selection of various contents (editorial and user-generated), free form discussion, knowledge base \\

  \hline
\end{tabularx}

@@

\begin{frame}[t]{Tools for an Online Community}

>>>>

%===============================================================================
\begin{frame}[t]{A (long) sentence for a UQ online community}

We aim our UQ online community to be a community of:

\begin{itemize}
  \item UQ practitioners and researchers and
  \item UQLab users
\end{itemize}

across different level of expertise, from beginners to advanced, to:

\begin{itemize}
  \item learn the basics as well as new things in UQ;
  \item discuss UQ-related topics, share news, knowledge and experience, and showcase expertise;
  \item get and give help in using UQLab and discuss UQLab features and its continuous development.
\end{itemize}

%\begin{tabularx}{\textwidth}{XX}
%  \hline
%  Questions                            & Answers \\
%  \hline
%  \emph{What will the community be about?}               & About UQ and UQLab-related topics \\
%  \emph{Who is the community for?}                       & UQ practitioners, researchers, and UQLab users \\

%  \emph{What is the purpose or goal of the community? What UQLab community strive for?}
%  & \tabitem Be a place to discuss about, share, learn, and get help in topics related to UQ, from beginners to advanced \\
%  & \tabitem Be the definitive community-powered home for UQLab support and best practices \\

%  \emph{What will happen in the community?}          & Selection of various contents (editorial and user-generated), free form discussion, knowledge base \\

%  \hline
%\end{tabularx}

@@

%===============================================================================
\begin{frame}[t]{Tools for an Online Community}
